%!TEX root = ../../main.tex
%----------------------------------------------------------------------------
\chapter{Conclusion}\label{chap:conclusion}
%----------------------------------------------------------------------------
Mobile robot\\
The tasks of the mobile platform was the transportation and loading of the LEGO bricks to be sorted. In transporting it would have to operate on two different kinds of navigation environments. One being guided by black lines and one in an unprepared area. The mobile robot system was able to successfully navigate in both these areas thus completing its transportation role. Though the execution during 24 hour test was not absolutely flawless it did perform reasonably well. A large contributor to navigation errors was traffic jam or collisions with other robot systems. 

The loading of bricks onto the conveyor was done by modifying the tipper on the original FrobitPro. After the modifications the transfer was achieved repeatedly  during the final test. 

All in all the mobile robot was able to go to the brick dispenser, transport bricks in the open area and along the guide lines to the conveyor where they were unloaded. It could then go to the robot to pick up the final order and transport it back to the charging station where it would stay and charge until battery level was sufficient for the next order.


The robot cell developed is able to; receive unsorted bricks from the mobile platform, pick the correct bricks according to order specification from MES server and placing the order back on the mobile robot. All this functionality can operate automatically or supervised by an user through the developed HMI. The 24 hour integration test showed a fairly stable Robot cell system with mostly minor errors which could be resolved and recovered from manually.

%test showed 9 errors with the robot cell out of 49 runs. 3 of the errors were resolved during the test, 3 errors was from external issues which the group have no control of. The last three 



%%% Local Variables:
%%% mode: latex
%%% TeX-master: "main"
%%% End:
